### 2023-04-06 main.tex
i

\begin{comment}
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\end{comment}
\subsubsection{The similarity transformation}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
\end{equation}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
\begin{equation}
    \mathcal{S}_{1}=S_{1}^{\otimes L}
\end{equation}
that is related with the duality matrix by 
\begin{equation}
\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
\end{equation}
 This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
\end{equation}
that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
\end{equation}
The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
\begin{equation}
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
\end{equation}
Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
\begin{equation}
	H^{'}|\Psi^{'}\rangle=0
\end{equation}
therefore, it is easy to see that 
\begin{equation}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
\end{equation}

@@

@@

\subsubsection{The steady state of $J^{''}$}\label{subsectionSSHsec}

@@

Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}. The result is the following 

@@

			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}

@@

\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. The matrix $S_{2}^{-1}$, acting on a single site, is given by 

@@

        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+Q
	Q:=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
We compute
        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
         I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
where the addends are 
	&I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}\\
	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}\\
	&Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}\\
	&Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}e_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $s_{1},s_{2}$ reads
	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
We iterate this tensor product for the chain of length $L$, and we write the raw with indices arbitrary $\bm{s}=s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$ as
	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$ that are given by 
\begin{equation}\label{ABS_intermediate}
		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
For a fixed configuration $\bm{s}=(s_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
  \left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)
we obtain 
\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS}.
\subsubsection{The steady state of $H$}\label{subsectionSSH}
The steady state $|\Psi\rangle$ of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 
\begin{equation}\label{steadyStateH}
    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
where for every $(s_{1},\ldots,s_{L})=\bm{s}$
\begin{equation}\label{steadyStateH-coeff}
        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
  \prod_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
 \\ &
 \beta_{s_{x}}^{(1-c_{x})(1-\delta_{s_{x},1})}
\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations, 
\begin{equation}\label{LinkABS-corr}
\Psi(\bm{s})=\widehat{\Psi}(\bm{s})

\paragraph{Proof of formula \eqref{steadyStateH}} To find $|\Psi\rangle$ we will use \eqref{SteadystateHat}. For the sake of notation we call

>>>>

\begin{comment}
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\end{comment}
\subsubsection{The similarity transformation}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
\end{equation}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
\begin{equation}
    \mathcal{S}_{1}=S_{1}^{\otimes L}
\end{equation}
that is related with the duality matrix by 
\begin{equation}
\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
\end{equation}
 This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
\end{equation}
that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
\end{equation}
The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
\begin{equation}
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
\end{equation}
Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
\begin{equation}
	H^{'}|\Psi^{'}\rangle=0
\end{equation}
therefore, it is easy to see that 
\begin{equation}\label{S1-Inverse}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
\end{equation}

@@

\begin{equation}\label{S2-Inverse}

@@

\subsubsection{The steady state of $H^{''}$}\label{subsectionSSHsec}

@@

Knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 

@@

			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}

@@

\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. The matrix $S_{2}^{-1}$, acting on a single site, is given by 

@@

    \begin{equation}\label{InverseS2}
    	\begin{split}
    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    		\right. \\&+ \left. 
    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
    	\end{split}
    \end{equation}
    We prove it by induction. When $L=1$ it is true, indeed
    \begin{equation}
    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    \end{equation}
    Assuming that \eqref{InverseS2} is true for $L$, we prove that it holds for $L+1$
\begin{align*}
    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    	\\&=
    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
    	\\&=
    	\left(S_{2}^{\otimes L+1}\right)^{-1}
\end{align*}
    \begin{comment}

    \begin{equation}
        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+Q
    \end{equation}
    where
    \begin{equation}
	Q:=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
\end{equation}
We compute
\begin{equation}
    \begin{split}
        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
         \\&=
         I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
    \end{split}
\end{equation}
where the addends are 
\begin{equation}
\begin{split}
	&I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}\\
	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}\\
	&Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}\\
	&Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}e_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
 \end{split}
\end{equation}
The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
\begin{equation}
	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
\end{equation}
where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $s_{1},s_{2}$ reads
\begin{equation}
	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
\end{equation}
\end{comment}
The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$. 
To find this elements we need to fix the rows correspondent to $\bm{s}$. Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\begin{equation}
	\begin{split}
	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
  \\&+
  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
	\end{split}
\end{equation}

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{s}=(s_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
\end{equation}
Introducing
\begin{equation}
	c_{x}=(1-\delta_{s_{x},1}) \qquad \forall x\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{s})$ compute above in \eqref{ABS_intermediate} we obtain
